Left-linear rewriting in adhesive categories

### 2024-04-23 concur/fusione.tex
typos

\begin{example}
  \label{ex:seq-ind}
  Consider a rewriting system in $\cat{Graph}$, the category of
  directed graphs and graph morphisms, which is adhesive. The set of
  rules $\R = \{ \rho_0, \rho_1, \rho_2\}$ consists of the three rules
  of Fig.~\ref{fi:rules}, where numbers are used to represent
  the morphisms from the interface to the left- and right-hand
  sides. Rules $\rho_0$ and $\rho_1$ are linear: $\rho_0$ generates a
  new node, while $\rho_1$ creates an edge. Instead, $\rho_2$ is
  left-linear but not linear, as it ``merges'' two nodes.\todo{P: se $\rho_0$ generasse un arco tra 1 e 2, poi le derivazioni $\der{D}$ e $\der{D}'$ che non vogliamo siano switch equivalent hanno grafi intermedi non isomorfi, non solo con isomorfismi non consistenti, che mi pare meglio. Da vedere.}

@@

  As a consequence, $\der{D}$ and $\der{D}'$ would be switch
  equivalent, but this is not acceptable when viewing equivalence
  classes of derivations as concurrent computations: in $\der{D}$ the
  first two steps are not sequential independent, while in $\der{D}'$
  they are, intuitively because in $\der{D}$ rule $\rho_1$ uses the
  node generated by $\rho_0$ (adding a self loop to it), while in
  $\der{D}'$ rule $\rho_1$ uses the node that was in the initial
  graph. From the technical point of view, the property of being
  switch equivalent is not closed by prefix, and this prevents
  to derive a sensible concurrent semantics: 
  In fact $\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
  $\der{D}' = \dder{D}_0'\cdot \dder{D}_1' \cdot \dder{D}_2'$ are switch 
  equivalent, while if we consider the first
  two steps, derivations $\dder{D}_0 \cdot \dder{D}_1$ and
  $\dder{D}_0' \cdot \dder{D}_1'$  are not switch equivalent.
  % if we limit to the first
  %two steps, we obtain derivations $\dder{D}_0 \cdot \dder{D}_1$ and
  %$\dder{D}_0' \cdot \dder{D}_1'$ that are not switch equivalent, while
  %$\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
  %$\der{D}' = \dder{D}_0'\cdot \dder{D}_1' \cdot \dder{D}_2'$ would
  %be.
\end{example}

>>>>

\begin{example}
  \label{ex:seq-ind}
  Consider a rewriting system in $\cat{Graph}$, the category of
  directed graphs and graph morphisms, which is adhesive. The set of
  rules $\R = \{ \rho_0, \rho_1, \rho_2\}$ is in
  Fig.~\ref{fi:rules}, where numbers are used to represent the
  morphisms from the interface to the left- and right-hand
  sides. Rules $\rho_0$ and $\rho_1$ are linear: $\rho_0$ generates a
  new node and a new edge, while $\rho_1$ creates a self-loops edge. Instead,
  $\rho_2$ is left-linear but not linear, as it ``merges'' two nodes.

@@

  As a consequence, $\der{D}$ and $\der{D}'$ would be switch
  equivalent, but this is not acceptable when viewing equivalence
  classes of derivations as concurrent computations: in $\der{D}$ the
  first two steps are not sequential independent, while in $\der{D}'$
  they are, intuitively because in $\der{D}$ rule $\rho_1$ uses the
  node generated by $\rho_0$ (adding a self loop to it), while in
  $\der{D}'$ rule $\rho_1$ uses the node that was in the initial
  graph. Also observe that the graphs $G_2$ and $G_2'$ produced after
  two steps in $\der{D}$ and $\der{D'}$ are not isomorphic. From the
  technical point of view, the property of being switch equivalent is
  not closed by prefix, and this prevents to derive a sensible
  concurrent semantics: In fact
  $\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
  $\der{D}' = \dder{D}_0'\cdot \dder{D}_1' \cdot \dder{D}_2'$ are
  switch equivalent, while if we consider the first two steps,
  derivations $\dder{D}_0 \cdot \dder{D}_1$ and
  $\dder{D}_0' \cdot \dder{D}_1'$ are not switch equivalent.
  % if we limit to the first
  %two steps, we obtain derivations $\dder{D}_0 \cdot \dder{D}_1$ and
  %$\dder{D}_0' \cdot \dder{D}_1'$ that are not switch equivalent, while
  %$\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
  %$\der{D}' = \dder{D}_0'\cdot \dder{D}_1' \cdot \dder{D}_2'$ would
  %be.
\end{example}
